Evaluation of the article

### 2024-11-04 pages/paper_evaluation.qmd
docs(paper evaluation): correction to huang and lim stress-des, and removing addressed TODO

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 6, 3, 1],
  'Lim et al. 2020': [16, 2, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [16, 1, 2, 5],
  'Hernandez et al. 2015': [18, 2, 3, 1],
  'Wood et al. 2021': [22, 2, 0, 0]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
plot_scatter('STRESS-DES criteria met',
             sho = (17/24)*100,
             hua = (14/23)*100,
             lim = (16/21)*100,
             kim = (15/22)*100,
             ana = (14/21)*100,
             joh = (16/19)*100,
             her = (18/23)*100,
             woo = (22/24)*100)
```

@@

<!-- TODO: update after discussion of Kim et al. 2021 -->

@@

| **4.3 Estimation approach**<br>State the method used to account for the stochasticity: For example, two common methods are multiple replications or batch means. Where multiple replications have been used, state the number of replications and for batch means, indicate the batch length and whether the batch means procedure is standard, spaced or overlapping. For both procedures provide a justification for the methods used and the number of replications/size of batches. | 🟡 | 🟡 | ✅ | ✅ | ✅ | N/A | ✅ | ✅ |

@@

| **5.2 Random sampling**<br>State the algorithm used to generate random samples in the software/programming language used e.g. Mersenne Twister.<br>If common random numbers are used, state how seeds (or random number streams) are distributed among sampling processes. | ❌ | 🟡 | ❌ | ❌ | ❌ | N/A | ❌ | ✅ |

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  '1.1 Purpose': [8, 0, 0, 0],
  '1.2 Outputs': [7, 1, 0, 0],
  '1.3 Aims': [7, 0, 0, 1],
  '2.1 Diagram': [8, 0, 0, 0],
  '2.2 Base logic': [8, 0, 0, 0],
  '2.3 Scenarios': [7, 0, 0, 1],
  '2.4 Algorithms': [6, 2, 0, 0],
  '2.5.1 Entities': [8, 0, 0, 0],
  '2.5.2 Activities': [8, 0, 0, 0],
  '2.5.3 Resources': [5, 0, 0, 3],
  '2.5.4 Queues': [5, 0, 0, 3],
  '2.5.5 Entry/Exit': [8, 0, 0, 0],
  '3.1 Data sources': [8, 0, 0, 0],
  '3.2 Pre-processing': [3, 0, 0, 5],
  '3.3 Inputs': [5, 3, 0, 0],
  '3.4 Assumptions': [6, 0, 2, 0],
  '4.1 Initialisation': [2, 2, 4, 0],
  '4.2 Run length': [7, 1, 0, 0],
  '4.3 Estimation': [5, 2, 0, 1],
  '5.1 Language': [0, 8, 0, 0],
  '5.2 Random': [1, 1, 5, 1],
  '5.3 Execution': [1, 1, 6, 0],
  '5.4 System': [1, 4, 3, 0],
  '6.1 Sharing': [8, 0, 0, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

Below, I've reflected on the impact of each criteria being fulfilled, on the reproduction. I've also identified where I feel I've been a bit more lax in my evaluation. <!-- TODO: Consider - is this an issue? Should I revisit those and be more strict? -->

@@

<!--TODO: Check Lim 2020 - think it should be changed to partially met, as no justification mentioned -->

@@

* Frequently not described, despite some of the studies having implemented and used seeds.

<!--TODO: Check Huang 2019, looks like I've answered with arrival sampling, but that is not relevant here - but does indicate that the wording here is a little confusing perhaps -->

>>>>

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 5, 4, 1],
  'Lim et al. 2020': [15, 3, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [16, 1, 2, 5],
  'Hernandez et al. 2015': [18, 2, 3, 1],
  'Wood et al. 2021': [22, 2, 0, 0]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

@@

```{python}
plot_scatter('STRESS-DES criteria met',
             sho = (17/24)*100,
             hua = (14/23)*100,
             lim = (15/21)*100,
             kim = (15/22)*100,
             ana = (14/21)*100,
             joh = (16/19)*100,
             her = (18/23)*100,
             woo = (22/24)*100)
```

@@

@@

| **4.3 Estimation approach**<br>State the method used to account for the stochasticity: For example, two common methods are multiple replications or batch means. Where multiple replications have been used, state the number of replications and for batch means, indicate the batch length and whether the batch means procedure is standard, spaced or overlapping. For both procedures provide a justification for the methods used and the number of replications/size of batches. | 🟡 | 🟡 | 🟡 | ✅ | ✅ | N/A | ✅ | ✅ |

@@

| **5.2 Random sampling**<br>State the algorithm used to generate random samples in the software/programming language used e.g. Mersenne Twister.<br>If common random numbers are used, state how seeds (or random number streams) are distributed among sampling processes. | ❌ | ❌ | ❌ | ❌ | ❌ | N/A | ❌ | ✅ |

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
  '1.1 Purpose': [8, 0, 0, 0],
  '1.2 Outputs': [7, 1, 0, 0],
  '1.3 Aims': [7, 0, 0, 1],
  '2.1 Diagram': [8, 0, 0, 0],
  '2.2 Base logic': [8, 0, 0, 0],
  '2.3 Scenarios': [7, 0, 0, 1],
  '2.4 Algorithms': [6, 2, 0, 0],
  '2.5.1 Entities': [8, 0, 0, 0],
  '2.5.2 Activities': [8, 0, 0, 0],
  '2.5.3 Resources': [5, 0, 0, 3],
  '2.5.4 Queues': [5, 0, 0, 3],
  '2.5.5 Entry/Exit': [8, 0, 0, 0],
  '3.1 Data sources': [8, 0, 0, 0],
  '3.2 Pre-processing': [3, 0, 0, 5],
  '3.3 Inputs': [5, 3, 0, 0],
  '3.4 Assumptions': [6, 0, 2, 0],
  '4.1 Initialisation': [2, 2, 4, 0],
  '4.2 Run length': [7, 1, 0, 0],
  '4.3 Estimation': [4, 3, 0, 1],
  '5.1 Language': [0, 8, 0, 0],
  '5.2 Random': [1, 0, 6, 1],
  '5.3 Execution': [1, 1, 6, 0],
  '5.4 System': [1, 4, 3, 0],
  '6.1 Sharing': [8, 0, 0, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

@@

Below, I've reflected on the impact of each criteria being fulfilled, on the reproduction. I've also identified where I feel I've been a bit more lax in my evaluation - indeed, the "subjective" nature of this evaluation is a limitation - although did (a) get consensus on uncertainties and unmet, and (b) revisit alongside other evaluations when writing this section, which helped me identify a few inconsistent decisions between studies within the evaluation, which I then addressed.

@@

@@

* Frequently not described, despite some of the studies having implemented and used seeds.
* Initially incorrectly addressed this in one of my evaluations, accidentally adding notes on the sampling of arrivals, rather than specifically on random samples. Have noted this to be clear that it was possible to misinterpret (although that may be more a mistake of my own! and not one others would necessarily make.)
